---
title: "Article graph"
author: "John Coene"
date: 2019-07-09T00:00:00+02:00
categories: ["R"]
tags: ["R Markdown", "weforum"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

r-news' first blog post 🎉

In this post we build a graph from articles of the World Economic Forum's [Agenda](https://www.weforum.org/agenda) where we attempt reveal underlying editorial themes.

We'll use just four packages, [weforum](https://github.com/news-r/weforum) which will allow us to download the articles of the Agenda then we'll use dplyr and purrr to process the data, and finally we'll use [sigmajs](http://sigmajs.john-coene.com) to visualise the graph.

First we'll fetch 7,500 articles.

```{r, echo=FALSE}
load("articles.RData")
```

```r
# remotes::install_github("news-r/weforum")
library(weforum)

articles <- wef_articles_list(pages = 300)

save(articles, file = "articles.RData")
```

The articles have 

```{r}
library(dplyr)
library(purrr)

ids <- articles %>% 
  map("id") %>% 
  unlist()

titles <- articles %>% 
  map("attributes") %>% 
  map("title") %>% 
  unlist()

title_id_keypair <- tibble::tibble(
  article_id = ids,
  article_title = titles
)

edges <- articles %>% 
  map("relationships") %>% 
  map("topics") %>% 
  map("data") %>% 
  flatten() %>% 
  map2(ids, function(x, y) {
    if(length(x))
      x$article_id <- y
    return(x)
  }) %>% 
  map_dfr(bind_rows)

edges <- edges %>% 
  left_join(title_id_keypair, by = "article_id")

library(sigmajs)

edges <- edges %>% 
  select(
    topic_id = id,
    topic_title = title,
    article_id,
    article_title
  ) %>% 
  mutate(
    topic_id = paste0("topic_", topic_id),
    article_id = paste0("article_", article_id)
  ) %>% 
  distinct() %>% 
  mutate(id = 1:n()) 

nodes <- edges %>% 
  select(id = topic_id, name = topic_title) %>% 
  bind_rows(
    edges %>% 
      select(id = article_id, name = article_title)
  ) %>% 
  count(id, name) %>% 
  mutate(
    type = case_when(
      grepl("article", id) ~ "article",
      TRUE ~ "topic"
    ),
    color = case_when(
      type == "article" ~ "#247BA0",
      TRUE ~ "#FF1654"
    )
  )

sigmajs() %>% 
  sg_nodes(nodes, id, label = name, size = n, color) %>% 
  sg_edges(edges, id, source = topic_id, target = article_id) %>% 
  sg_settings(
    minNodeSize = 1,
    maxNodeSize = 5,
    edgeColor = "default",
    defaultEdgeColor = "rgba(211, 211, 211, 0.2)",
    batchEdgesDrawing = TRUE
  ) %>% 
  # sg_cluster(colors = c("#247BA0", "#70C1B3", "#B2DBBF", "#F3FFBD", "#FF1654")) %>% 
  sg_force_start() %>% 
  sg_force_stop(25000) %>% 
  sg_neighbours()
```